Tables

### 2023-09-08 output/paper/figures.qmd
Added details for paper if published in EHP. Still no line numbering in DOCX nor PDF.

---
title: "Paper 3 - Figures"

@@

<!-- ####################################################################### -->
# CTD Results
<!-- ####################################################################### -->
```{r}
#| label: fig-ctd-res
#| fig.cap: Barplot CTD.
#| fig.height: 10
#| fig.width: 10
path <- "results/files/CTD_chem_diseases_1680702221550_05042023.csv"
ctd <- myphd::load_ctd(path = path, 
                       filter_evidence = TRUE)
myphd::plot_ctd(ctd)
```

>>>>

---
title: "Figures"

@@

- Number figures according to the order in which they are first mentioned in the main text.
- Clearly label all axes, giving both the measure and the unit of measurement.
- Not larger than 7.5 inches in width.
- Save and submit each main text figure as an individual file (PDF with fonts embedded). Include the figure number in the file name of each figure.
- Provide main text figure captions on a new page of the main text after the tables.
- Include a title for the entire figure and descriptors for each panel.

# CTD Results
```{r}
#| label: fig-ctd-res
#| fig.cap: Barplot CTD.
#| fig.height: 10
#| fig.width: 10

path <- "results/files/CTD_chem_diseases_1680702221550_05042023.csv"
ctd <- myphd::load_ctd(path = path, 
                       filter_evidence = TRUE)
myphd::plot_ctd(ctd)
```

### 2023-09-08 output/paper/manuscript.qmd
Added details for paper if published in EHP. Still no line numbering in DOCX nor PDF.

format:
  pdf:
    pdf-engine: xelatex
    number-sections: true
    toc: false
    include-in-header:
      text: |
        \usepackage{rotating}
        \usepackage{float}
        \usepackage{typearea}

bibliography: ../../../../PhD.bib
link-citations: true
linkcolor: blue

execute:
  echo: false
  warning: false
  error: false
  message: false
editor_options: 
  chunk_output_type: console

filters:
  - ../../../../all_phd/_extensions/acronyms/parse-acronyms.lua
  - ../../../../all_phd/_extensions/authors-block/authors-block.lua
acronyms:
  fromfile: ../../../../all_phd/acronyms.yml
  insert_links: false
  insert_loa: false
  sorting: alphabetical

@@

 **Discussion**
---

@@

---
title: "Some Title"
---

<!-- ####################################################################### -->
# Introduction {#intro}
```{r}
#| child: output/paper/sections/introduction.qmd
```
<!-- ####################################################################### -->

<!-- ####################################################################### -->
# Methods {#methods}
```{r}
#| child: output/paper/sections/methods.qmd
```
<!-- ####################################################################### -->

<!-- ####################################################################### -->
# Results {#res}
```{r}
#| child: output/paper/sections/results.qmd
```
<!-- ####################################################################### -->

<!-- ####################################################################### -->
# Discussion {#discussion}
```{r}
#| child: output/paper/sections/discussion.qmd
```
<!-- ####################################################################### -->

@@

<!-- ####################################################################### -->
# References {.unnumbered}
<!-- ####################################################################### -->

>>>>

format:
  docx:
    reference-doc: reference_document.docx
  pdf:
    pdf-engine: lualatex
    number-sections: true
    toc: false
    include-in-header:
      text: |
        \usepackage{rotating}
        \usepackage{float}
        \usepackage{typearea}
        \usepackage{lineno}

@@

 **Discussion**

bibliography: bibliography.bib
csl: ama11.csl

link-citations: true
linkcolor: blue

editor_options: 
  chunk_output_type: console

filters:
  - ../../../../all_phd/_extensions/acronyms/parse-acronyms.lua
  - ../../../../all_phd/_extensions/authors-block/authors-block.lua
  - ../../../../all_phd/_extensions/wordcount/citeproc.lua
  - ../../../../all_phd/_extensions/wordcount/wordcount.lua

acronyms:
  fromfile: ../../../../all_phd/acronyms.yml
  insert_links: false
  insert_loa: false
  sorting: alphabetical

execute:
  echo: false
  warning: false
  error: false
  message: false
---

@@

---
title: "Some Fancy Title"
---

- The title should be less or equal than 300 characters. It should indicate the study design, the subject of the paper, information regarding exposures and outcomes assessed, and whether the study was observational or experimental.
- The suggested length of the abstract is less or equal than 300 words.
- The suggested length is <7,000 words, excluding abstract, references, tables, figure captions, acknowledgments, and Supplementary Material.
  - Concise sub-headings should be less or equal than 8 words, and they should be used to organize information rather than summarize the results.
  - In-text citations with superscript numbers: outside periods and commas, but inside colons and semicolons.

# Introduction {#sec-intro}
```{r}
#| child: output/paper/sections/introduction.qmd
```

# Methods {#sec-methods}
```{r}
#| child: output/paper/sections/methods.qmd
```

# Results {#sec-res}
```{r}
#| child: output/paper/sections/results.qmd
```

# Discussion {#sec-discussion}
```{r}
#| child: output/paper/sections/discussion.qmd
```

@@

# Funding

- Give the source of funding and the role of the funders for the present study and, if applicable, for the original study on which the present article is based.

# References {.unnumbered}

### 2023-09-08 output/paper/sections/discussion.qmd
Added details for paper if published in EHP. Still no line numbering in DOCX nor PDF.

List of possible limitations:

* The percentiles of the exposures might differ considerably by cohort. When using `avg_comparisons`, we do not consider this. This might cause cohort-dependent positivity issues (?).

>>>>

## Key results {#sec-disc-res-key}

- Summarise key results with reference to study objectives.
- Provide a review of the relevant literature to put the study findings into context.
  - It should be complete and balanced, including inconsistent results.
  - It should include, for each source, sufficient details: study design, sample size, population, specific exposures and outcomes.

## Limitations {#sec-limitations}

- Discuss limitations of the study, taking into account sources of potential bias or imprecision.
- Discuss both direction and magnitude of any potential bias.

## Interpretation {#sec-interpretation}

- End with a summary of the key findings and their implications for the study hypotheses, future research, and policy.
- Give a cautious overall interpretation of results considering objectives, limitations, multiplicity of analyses, results from similar studies, and other relevant evidence.

## Generalisability {#sec-general}

- Discuss the generalisability (external validity) of the study results.

### 2023-09-08 output/paper/sections/methods.qmd
Added details for paper if published in EHP. Still no line numbering in DOCX nor PDF.

## Study population {#sec-study-population}

## Exposure assessment {#sec-exp-assessment}

## Metabolomics {#sec-metabolomics}

## Neurodevelopment {#sec-neurodevelopment}

## Covariates {#sec-covars}

## Statistical analysis {#sec-stat-analysis}

>>>>

## Study design {#sec-design}

- Present key elements of study design

## Setting {#sec-setting}

- Describe the setting, locations, and relevant dates, including periods of recruitment, exposure, follow-up, and data collection.

## Participants {#sec-participants}

- Cohort study: eligibility criteria, and the sources and methods of selection of participants. Describe methods of follow-up.
- Cross-sectional study: give eligibility criteria, and the sources and methods of selection of participants.
- Describe informed consent protocols.
- Report how and by whom *race* or *ethnicity* was defined, and why this information was included in the study design. Disaggregate race and ethnicity data to the fullest extent possible.

## Variables {#sec-vars}

- Clearly define all outcomes, exposures, predictors, potential confounders, and effect modifiers.
- Explain the rationale for treating race as an exposure, confounder, effect modifier, or other type of variable in analyses.

### Confounders {#sec-confounders}

### Endocrine disrupting chemicals {#sec-edcs}

### Corticosteroids {#sec-steroids}

### Neurodevelopment {#sec-neurodevelopment}

## Data sources and measurement {#sec-dat-sources}

- For each variable of interest, give sources of data and details of methods of assessment (measurement).

## Bias {#sec-bias}

- Describe any efforts to address potential sources of bias.

## Study size {#sec-size}

- Explain how the study size was arrived at.

## Quantitative variables {#sec-quant-vars}

- Explain how quantitative variables were handled in the analyses. If applicable, describe which groupings were chosen and why.

## Statistical methods {#sec-stat-methods}

- Methods for selecting potential confounders (provide DAGs).
- Describe all statistical methods with assumptions, including those used to control for confounding.
- Describe any methods used to examine subgroups and interactions.
- Explain how missing data were addressed.
- Cohort study: explain how loss to follow-up was addressed.
- Cross-sectional study: describe analytical methods taking account of sampling strategy.
- Describe any sensitivity analyses.
- When referring to previous publications for methods' details, include a brief description of the approach, key assumptions and limitations, and any deviation.
- Names and version numbers for the used software packages, including non-data arguments if deviating from the default ones.

### 2023-09-08 output/paper/si.qmd
Added details for paper if published in EHP. Still no line numbering in DOCX nor PDF.

---
title: "Paper 3 - Supplementary Information"

@@

@@

>>>>

---
title: "Supplementary Material"

@@

bibliography: bibliography.bib
csl: ama11.csl

@@

- Should be limited to results of secondary analyses and background details needed to ensure transparency:
  - Questionnaires.
  - Tables and figures with results of sensitivity analyses.
  - Tables with numeric data corresponding to results shown in the main text figures.
  - DAGs used to select model covariates.
- Text description of study methods should NOT go in the SM.
- Order the content: text, supplemental tables, and supplemental figures.
- Provide the title for each figure below the figure on the same manuscript page as the figure itself.
- Provide the title for each table above the table and the notes below the table.
- Number supplemental tables and figures separately according to the order in which they are first mentioned in the main text, using an "S" prefix.
- Conclude the SM with a list of references, even if they are also cited in the main paper.

### 2023-09-08 output/paper/tables.qmd
Added details for paper if published in EHP. Still no line numbering in DOCX nor PDF.

---
title: "Paper 3 - Tables"

@@

<!-- ####################################################################### -->
# Study populations
<!-- ####################################################################### -->
```{r}

@@

<!-- ####################################################################### -->
# Exposures
<!-- ####################################################################### -->
```{r}
#| label: tbl-chem-info
#| tbl-cap: Information about the non-persistent EDCs.
edcs_info <- myphd::edcs_information() |>
  tidylog::select(-c(chem_id, smiles))
gt::gt(edcs_info, groupname_col = "class") |>
  gt::cols_label(
    full_name = "Compound", 
    short_name = "Symbol", 
    pubchem_cid = "PubChem CID", 
    ctd_id = "CTD ID", 
    exposome_explorer_id = "Exposome Explore ID", 
    parental_compound = "Parental compound"
  ) |>
  gt::tab_style(
    locations = gt::cells_column_labels(columns = everything()), 
    style = list(
      gt::cell_borders(sides = "bottom", weight = gt::px(3)), 
      gt::cell_text(weight = "bold")
    )
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()), 
    style = list(gt::cell_text(weight = "bold"))
  )
```

>>>>

---
title: "Tables"

@@

- Begin each table on a new page after the list of references.
- Tables may not contain parts.
- List footnotes after the general one, one per line and indicated with a lowercase italicized letter.

# Study populations
```{r}

@@

# Exposures
```{r}
#| label: tbl-chem-info
#| tbl-cap: Information about the non-persistent EDCs.

edcs_info <- myphd::edcs_information() |>
  tidylog::select(-c(chem_id, smiles))
gt::gt(edcs_info, groupname_col = "class") |>
  gt::cols_label(
    full_name = "Compound", 
    short_name = "Symbol", 
    pubchem_cid = "PubChem CID", 
    ctd_id = "CTD ID", 
    exposome_explorer_id = "Exposome Explore ID", 
    parental_compound = "Parental compound"
  ) |>
  gt::tab_style(
    locations = gt::cells_column_labels(columns = everything()), 
    style = list(
      gt::cell_borders(sides = "bottom", weight = gt::px(3)), 
      gt::cell_text(weight = "bold")
    )
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()), 
    style = list(gt::cell_text(weight = "bold"))
  )
```
